Yeast RNA-seq 48 sample simulation study

### 2018-03-27 datasets/RNA-Seq/yeast-simulation.Rmd
Standardize and update covariate plots
Change paste0 to file.path, rename covariate Heatmap function to
covariateLinePlot.

```{r, results='hide', message=FALSE}
# Load packages and source benchmark FDR
library(data.table)
library(tidyr)
library(dplyr)
library(readr)
library(ggplot2)
library(magrittr)
library(R.utils)
library(cowplot)
library(purrr)
library(DESeq2)
library(tibble)
library(ggthemes)

# benchmark methods
library(IHW)
library(ashr)
library(qvalue)
library(swfdr)
library(fdrtool)
library(FDRreg)

# comparison tools/functions
library(SummarizedBenchmark)
sourceDirectory("../R/")

@@

```{r, download}
download.file(url = "https://github.com/bartongroup/profDGE48/raw/master/Preprocessed_data/Snf2_countdata.tar.gz",
              destfile = paste0(datdir, "/Snf2_countdata.tar.gz"))
download.file(url = "https://github.com/bartongroup/profDGE48/raw/master/Preprocessed_data/WT_countdata.tar.gz", 
              destfile = paste0(datdir, "/WT_countdata.tar.gz"))

gunzip(paste0(datdir, "/Snf2_countdata.tar.gz")) 
gunzip(paste0(datdir, "/WT_countdata.tar.gz"))

untar(paste0(datdir, "/Snf2_countdata.tar"), exdir = datdir) 
untar(paste0(datdir, "/WT_countdata.tar"), exdir = datdir)

file.remove(paste0(datdir, "/Snf2_countdata.tar"), 
            paste0(datdir, "/WT_countdata.tar"))
```

@@

```{r, results='hide', message=FALSE}
rseed <- 225
sampleSize <- 5
nDE <- 0
resfile <- paste0(resdir, "/null5.rds")

@@

covariateHeatmap(null5, alpha=0.05, covname="log2FC", trans="log1p")
covariateHeatmap(null5, alpha=0.05, covname="ind_covariate", trans="log1p")

covariateHeatmap(null5, alpha=0.05, covname="log2FC", nbins=25, 
                 trans="log1p", linePlot = TRUE)
covariateHeatmap(null5, alpha=0.05, covname="ind_covariate", nbins=25, 
                 linePlot = TRUE, trans="log1p")

@@

```{r, results='hide', message=FALSE}
rseed <- 837
sampleSize <- 10
nDE <- 0
resfile <- paste0(resdir, "/null10.rds")

@@

covariateHeatmap(null10, alpha=0.05, covname="log2FC", trans="log1p")
covariateHeatmap(null10, alpha=0.05, covname="ind_covariate", trans="log1p")

covariateHeatmap(null10, alpha=0.05, covname="log2FC", nbins=25, 
                 trans="log1p", linePlot = TRUE)
covariateHeatmap(null10, alpha=0.05, covname="ind_covariate", nbins=25, 
                 linePlot = TRUE, trans="log1p")

@@

```{r, results='hide', message=FALSE}
rseed <- 198
sampleSize <- 5
nDE <- 500
resfile <- paste0(resdir, "/de5.rds")

@@

covariateHeatmap(de5, alpha=0.05, covname="log2FC", trans="log1p")
covariateHeatmap(de5, alpha=0.05, covname="ind_covariate")

covariateHeatmap(de5, alpha=0.05, covname="log2FC", nbins=25, 
                 trans="log1p", linePlot = TRUE)
covariateHeatmap(de5, alpha=0.05, covname="ind_covariate", nbins=25, 
                 linePlot = TRUE)

@@

```{r, results='hide', message=FALSE}
rseed <- 961
sampleSize <- 10
nDE <- 500
resfile <- paste0(resdir, "/de10.rds")

@@

covariateHeatmap(de10, alpha=0.05, covname="log2FC", trans="log1p")
covariateHeatmap(de10, alpha=0.05, covname="ind_covariate")

covariateHeatmap(de10, alpha=0.05, covname="log2FC", nbins=25, 
                 trans="log1p", linePlot = TRUE)
covariateHeatmap(de10, alpha=0.05, covname="ind_covariate", nbins=25, 
                 linePlot = TRUE)

>>>>

```{r, results='hide', message=FALSE}
# Load packages and source benchmark FDR
library(data.table)
library(tidyr)
library(dplyr)
library(readr)
library(ggplot2)
library(magrittr)
library(cowplot)
library(purrr)
library(DESeq2)
library(tibble)
library(ggthemes)

## load helper functions
for (f in list.files("../R", "\\.(r|R)$", full.names = TRUE)) {
    source(f)
}

@@

```{r, download}
download.file(url = "https://github.com/bartongroup/profDGE48/raw/master/Preprocessed_data/Snf2_countdata.tar.gz",
              destfile = file.path(datdir, "Snf2_countdata.tar.gz"))
download.file(url = "https://github.com/bartongroup/profDGE48/raw/master/Preprocessed_data/WT_countdata.tar.gz", 
              destfile = file.path(datdir, "WT_countdata.tar.gz"))

gunzip(file.path(datdir, "Snf2_countdata.tar.gz")) 
gunzip(file.path(datdir, "WT_countdata.tar.gz"))

untar(file.path(datdir, "Snf2_countdata.tar"), exdir = datdir) 
untar(file.path(datdir, "WT_countdata.tar"), exdir = datdir)

file.remove(file.path(datdir, "Snf2_countdata.tar"), 
            file.path(datdir, "WT_countdata.tar"))
```

@@

```{r, results='hide', message=FALSE}
rseed <- 225
sampleSize <- 5
nDE <- 0
resfile <- file.path(resdir, "null5.rds")

@@

covariateLinePlot(null5, alpha=0.05, covname="log2FC", nbins=25, 
                 trans="log1p")
covariateLinePlot(null5, alpha=0.05, covname="ind_covariate", nbins=25, 
                 trans="log1p")

@@

```{r, results='hide', message=FALSE}
rseed <- 837
sampleSize <- 10
nDE <- 0
resfile <- file.path(resdir, "null10.rds")

@@

covariateLinePlot(null10, alpha=0.05, covname="log2FC", nbins=25, 
                 trans="log1p")
covariateLinePlot(null10, alpha=0.05, covname="ind_covariate", nbins=25, 
                 trans="log1p")

@@

```{r, results='hide', message=FALSE}
rseed <- 198
sampleSize <- 5
nDE <- 500
resfile <- file.path(resdir, "de5.rds")

@@

covariateLinePlot(de5, alpha=0.05, covname="log2FC", nbins=25, 
                 trans="log1p")
covariateLinePlot(de5, alpha=0.05, covname="ind_covariate", nbins=25, 
                 trans="log1p")

@@

```{r, results='hide', message=FALSE}
rseed <- 961
sampleSize <- 10
nDE <- 500
resfile <- file.path(resdir, "de10.rds")

@@

covariateLinePlot(de10, alpha=0.05, covname="log2FC", nbins=25, 
                 trans="log1p")
covariateLinePlot(de10, alpha=0.05, covname="ind_covariate", nbins=25, 
                 trans="log1p")
